---
title: "NYCOpenData"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(utils)
library(rvest)
library(stringi)
library(jsonlite)
library(geoclient)
library(gsheet)
library(janitor)
library(sf)
library(geojsonsf)
library(tigris)
library(urbnthemes)
library(urbnmapr)
library(leaflet)

set_urbn_defaults(style = "print")

knitr::opts_chunk$set(echo = TRUE)

geoclient_api_key(key = "1f02b4033c75431bbba245d5e8015a93")
```
# Pull in Data

## Get current open streets

```{r}
nyc_openstreets <- read.csv("https://data.cityofnewyork.us/api/views/uiay-nctu/rows.csv?accessType=DOWNLOAD") %>% 
  mutate(id = row_number(),
         Borough = tolower(Borough))
```

```{r}
count(nyc_openstreets, Borough)

```
# geocode nyc open portal data intersections
```{r}

nyc_intersections <- nyc_openstreets %>% 
  mutate(geo_from = geo_intersection(cross_street_1 = On.Street,
                        cross_street_2 = From.Street,
                        borough = Borough),
         lat_from = geo_from$latitude,
         long_from = geo_from$longitude,
         geo_to = geo_intersection(cross_street_1 = On.Street,
                        cross_street_2 = To.Street,
                        borough = Borough),
         lat_to = geo_to$latitude,
         long_to = geo_to$longitude) %>% 
  select(-geo_from, -geo_to)%>% 
  clean_names() %>% 
  mutate_if(is.character, tolower)


```




## Get Trans Alt Data

```{r}

taurl <- construct_download_url(url = "https://docs.google.com/spreadsheets/d/1eLDRtRGMPMrL5ZOYeKX-BbHTm6fCgmu1gayiVhQqH4A/edit#gid=1931274377")

tatbl <- gsheet2tbl(url = taurl, sheetid = "Open Streets Details")

var_names <- tatbl %>% 
  as.tibble() %>% 
  slice(1) %>% 
  unlist(., use.names = FALSE)

tadata <- tatbl %>% 
  filter(row_number()!=1)

colnames(tadata) = var_names
  
tadata <- tadata %>%
    clean_names() %>%
    mutate(id = row_number()) %>% 
    mutate_if(is.character, tolower)

write.csv("Open Streets Forever Report Crosstabs - Open Streets Details.csv")
```

## Get Chris Whong Live Data shapefile

```{r}
download.file("https://api.qri.cloud/ds/get/chriswhong/nyc-open-streets?format=zip", destfile = "open_streets_shape.zip", mode = "wb")
unzip("open_streets_shape.zip")

whong_live_streets_df <- read.csv("body.csv", header = FALSE, col.names = c("geometry", "feature_id", "location_or_partner", "borough", "on_street",
                                                                   "from_street", "to_street","type","open_date", "start_time", 
                                                                   "end_time","day_of_week", "neighborhood_name", "symbol", "shape_length", 
                                                                   "length_in", "shape_length_2")) %>% 
  clean_names() %>% 
  mutate_if(is.character, tolower)
```

data from: https://qri.cloud/chriswhong/nyc-open-streets 
```{r}

url_geojson <- "https://services.arcgis.com/wmZOI9vyUBq1zTZx/arcgis/rest/services/Open_Streets_Dissolve_FS/FeatureServer/0/query?where=1%3D1&objectIds=&time=&geometry=&geometryType=esriGeometryEnvelope&inSR=&spatialRel=esriSpatialRelIntersects&resultType=none&distance=0.0&units=esriSRUnit_Meter&returnGeodetic=false&outFields=*&returnGeometry=true&featureEncoding=esriDefault&multipatchOption=xyFootprint&maxAllowableOffset=&geometryPrecision=&outSR=&datumTransformation=&applyVCSProjection=false&returnIdsOnly=false&returnUniqueIdsOnly=false&returnCountOnly=false&returnExtentOnly=false&returnQueryGeometry=false&returnDistinctValues=false&cacheHint=false&orderByFields=&groupByFieldsForStatistics=&outStatistics=&having=&resultOffset=&resultRecordCount=&returnZ=false&returnM=false&returnExceededLimitFeatures=true&quantizationParameters=&sqlFormat=none&f=pgeojson&token="

whong_live_streets_sf <- geojson_sf(url_geojson)%>% 
  clean_names() %>% 
  mutate_if(is.character, tolower) %>% 
  rename(location_or_partner = location_p)


```
# try to merge these three different datasets into one
```{r}

whong_nyc <- full_join(nyc_intersections, whong_live_streets_sf, by = c("borough", "location_or_partner"))

ta_nyc <- full_join(nyc_intersections, tadata, by = c("borough", "location_or_partner", "on_street", "from_street", "to_street"))

ta_whong <- full_join(tadata, whong_live_streets_sf, by = c("borough", "location_or_partner"))

ta_shapes <- left_join(tadata, live_streets, by = c("borough", "location_or_partner"))

ta_mismatch <- anti_join(tadata, live_streets, by = c("borough", "location_or_partner"))
  
```


# geocode ta data intersections
```{r}

tadata_clean <- tadata  %>% 
    separate(on_street, sep = "/", into = c("on_street_1", "on_street_2", "on_street_3")) %>% 
    pivot_longer(cols = starts_with("on_street"), values_to = "on_street", names_to = "on_number") %>% 
    filter(!is.na(on_street)) %>% 
    separate(from_street, sep = "/", into = c("from_street_1", "from_street_2")) %>% 
    pivot_longer(cols = starts_with("from_street"), values_to = "from_street", names_to = "from_number") %>% 
    filter(!is.na(from_street)) %>% 
    mutate(from_street = case_when(
            from_street == "Washington Park Street" ~ "Washington Park",
            from_street == "Horace Harding" ~ "Horace Harding Expressway",
            T~from_street
          ),
          on_street = case_when(
            on_street == "Reservoir Oval East and West" ~ "Reservoir Oval",
            T~on_street
          ))



intersections <- tadata_clean %>% 
  mutate(geo_from = geo_intersection(cross_street_1 = on_street,
                        cross_street_2 = from_street,
                        borough = borough),
         lat_from = geo_from$latitude,
         long_from = geo_from$longitude,
         geo_to = geo_intersection(cross_street_1 = on_street,
                        cross_street_2 = to_street,
                        borough = borough),
         lat_to = geo_to$latitude,
         long_to = geo_to$longitude) %>% 
  select(-geo_from, -geo_to) #%>% 
  #mutate_if(is.character, tolower)


view_misses <- intersections %>% select(id, borough, location_or_partner, from_street,lat_from, long_from, on_street, to_street, lat_to, long_to) %>% 
  filter(is.na(lat_from)|is.na(lat_to)) %>% 
  arrange(lat_from, desc(lat_to))



```
# for missing/unmatched intersections, use TA's "nearby address field"
```{r}

addresses <- tadata %>% 
  geo_search_data(nearby_address) %>% 
  rename(nearby_address = input_location) %>% 
  select(nearby_address, latitude, longitude)

tadata_points <- left_join(tadata, addresses, by = "nearby_address") %>% 
  filter(!is.na(latitude)|!is.na(longitude)) %>% 
  select(id, latitude, longitude)
  
intersections_filled <- left_join(intersections, tadata_points, by = "id", suffix = c("", "_address") ) %>% 
  mutate(lat_from = if_else(is.na(lat_from), latitude, lat_from),
         long_from = if_else(is.na(long_from), longitude, long_from),
         lat_to = if_else(is.na(lat_to), latitude, lat_to),
         long_to = if_else(is.na(long_to), longitude, long_to))

count(intersections_filled, is.na(lat_from), is.na(lat_to), is.na(long_from), is.na(long_to))

intersections_lines <- intersections_filled %>%
  filter(!is.na(lat_from) & !is.na(lat_to) & !is.na(long_from) & !is.na(long_to)) %>% 
  select(starts_with("long_")|starts_with("lat_"), id)

from <- intersections_lines %>% select("long_from", "lat_from") %>% 
  rename(long = "long_from", lat = "lat_from")

to <- intersections_lines %>% select("long_to", "lat_to") %>% 
  rename(long = "long_to", lat = "lat_to")

intersections_lines$geometry = do.call(
  "c",
  lapply(seq(nrow(from)), function(i) {
    st_sfc(
      st_linestring(
        as.matrix(
          rbind(from[i, ], to[i, ])
        )
      ),
      crs = 4326
    )
  })
)

lines_sf <- st_as_sf(intersections_lines)

ta_open_streets_sf <- left_join(intersections_filled, lines_sf, by = "id") %>% 
  st_as_sf()

```
# Get elements for map
```{r}

nyc_counties <- c("005", "047", "061", "081", "085") #fips for NYC counties


nyc_water <- nyc_counties %>% 
  map(~area_water("NY", .x)) %>% 
  reduce(rbind) %>% 
  st_set_crs(st_crs(open_streets_sf))

coastline <- coastline()

nyc_roads <- nyc_counties %>% 
  map_dfr(~roads("NY", .x)) %>% 
  filter(RTTYP %in% c("C", "I", "S", "U", "O"))

nyc_outlines <- counties(state = "NY") %>% 
  filter(COUNTYFP %in% nyc_counties)
  

```

# Plot map of all streets

```{r}

ggplot()+
    geom_sf(data = nyc_outlines, mapping = aes(), fill = "dark grey", color = NA)+
    geom_sf(data = nyc_water, mapping = aes(), fill = "#030531", color = NA)+
    geom_sf(data = nyc_roads, mapping = aes(), color = "light grey", color = NA)+
    geom_sf(data = open_streets_sf, mapping = aes(), color = "#FFAB40")+
    #scale_color_manual(values = c("#55B748", "#db2b27"))+
    #geom_sf_text(data = nyc_outlines, mapping = aes(label = NAMELSAD))+
    theme(
    panel.grid = element_blank(),
    axis.line.x = element_blank(),
    axis.line.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text = element_blank(),
    plot.background = element_rect(fill = "#030531"),
    legend.text = element_text(color = "white"),
    plot.margin=grid::unit(c(0,0,0,0), "mm")
  )+
  guides(fill = guide_colourbar(barwidth = 10, barheight = 0.5))

ggsave("allstreets.png",
       device = "png",
       #width = 4.5,
       #height = 4.5
       )


```
# Map of active streets according to TA

```{r}

ggplot()+
    geom_sf(data = nyc_outlines, mapping = aes(), fill = "dark grey", color = NA)+
    geom_sf(data = nyc_water, mapping = aes(), fill = "#030531", color = NA)+
    geom_sf(data = nyc_roads, mapping = aes(), color = "light grey", color = NA)+
    geom_sf(data = open_streets_sf, mapping = aes(color = active_vs_non_operational))+
    scale_color_manual(values = c("#55B748", "#db2b27"))+
    #geom_sf_text(data = nyc_outlines, mapping = aes(label = NAMELSAD))+
    theme(
    panel.grid = element_blank(),
    axis.line.x = element_blank(),
    axis.line.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text = element_blank(),
    plot.background = element_rect(fill = "#030531"),
    legend.text = element_text(color = "white"),
    plot.margin=grid::unit(c(0,0,0,0), "mm")
  )+
  guides(fill = guide_colourbar(barwidth = 10, barheight = 0.5))

ggsave("activestreets.png",
       device = "png",
       #width = 4.5,
       #height = 4.5
       )


```

# Join between whong data and TA data

```{r}
ggplot()+
    geom_sf(data = nyc_outlines, mapping = aes(), fill = "dark grey", color = NA)+
    geom_sf(data = nyc_water, mapping = aes(), fill = "#030531", color = NA)+
    geom_sf(data = nyc_roads, mapping = aes(), color = "light grey", color = NA)+
    geom_sf(data = sf_live_streets, mapping = aes(), color = "#FFAB40")+
    geom_sf(data = open_streets_sf, mapping = aes(color = active_vs_non_operational), alpha = 0.5)+
    scale_color_manual(values = c("#55B748", "#db2b27"))+
    #scale_color_manual(values = c("#55B748", "#db2b27"))+
    #geom_sf_text(data = nyc_outlines, mapping = aes(label = NAMELSAD))+
    theme(
    panel.grid = element_blank(),
    axis.line.x = element_blank(),
    axis.line.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text = element_blank(),
    plot.background = element_rect(fill = "#030531"),
    legend.text = element_text(color = "white"),
    plot.margin=grid::unit(c(0,0,0,0), "mm")
  )+
  guides(fill = guide_colourbar(barwidth = 10, barheight = 0.5))
```
```{r}
leaflet() %>% addProviderTiles("CartoDB.Positron") %>% setView(lng = -74.0, lat = 40.7, zoom = 8.4) %>% 
  addTiles() %>% 
  addPolylines(data = ta_open_streets_sf) %>% 
  addPolylines(data = sf_live_streets, color = "#00FF00", opacity = 0.5)
  
```



```{r}
point_match <- st_intersects(sf_live_streets, open_streets_sf)

```





